Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-07 hscc2017/paper.tex
SC^2
nudges

\title{
Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous
Plants%
\thanks{Supported by EPSRC grant EP/J012564/1
and ERC project 280053 (CPROVER).}}

@@

\begin{abstract}
%
Modern control is implemented with digital microcontrollers, which are
designed to work in an embedded environment, within a dynamical plant that
represents physical components.
%
We present a new algorithm based on counter\-example guided inductive
synthesis that automates the design of digital controllers that are
correct by construction.  The synthesis result is sound with respect to the
complete range of approximations, including time discretization,
quantization effects, and finite-precision arithmetic and their related
rounding errors.
%
We have implemented our new algorithm in a tool called \tool, and are able
to automatically generate stable controllers for a set of intricate plant
models taken from the literature within minutes.
%
\end{abstract}

@@

\keywords{Control synthesis, CEGIS, finite word length, time sampling, quantization, interval analysis}

@@

Modern implementations of embedded control systems have proliferated with the
availability of low-cost devices that can perform highly non-trivial control
tasks, with significant impact in numerous application areas such as
environmental control and robotics~\cite{astrom1997computer, Franklin15}.
Correct and sound control is non-trivial, however. The problem is exacerbated by
artefacts specific to digital control, such as the effects of
finite-precision arithmetic, time discretization, and quantization noise
introduced by A/D and D/A conversion.  Thus, the programming is a key
barrier to broad adoption of digital control, and requires considerable
expertise.

@@

By contrast, we leverage a very recent step-change in the scalability of
\emph{program synthesis}.  Program synthesis engines use a program
specification as the starting point, and subsequently generate a sequence of
candidate programs.  The candidate programs are iteratively refined to match
the specification more closely.  Program synthesizers that implement
Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} are now
able to generate programs for highly non-trivial specifications with a very
high degree of automation.  Modern CEGIS engines combine automated testing,
genetic algorithms and SMT-based automated
reasoning~\cite{DBLP:conf/lpar/DavidKL15, DBLP:conf/cav/0001A14}.

By applying a state-of-the-art CEGIS engine we are now able to present a
tool that automatically \emph{generates} digital controllers for a given
continuous plant model that are correct by construction.  This approach
promises to reduce the cost and time of development of digital control
dramatically, and requires considerably less expertise than methodologies
driven by verification.  Specifically, we synthesize controllers for hybrid
closed-loop systems, i.e., software-implemented embedded controllers along
with a model of their physical environment (the plant), that are
\emph{stable}.  Due to the complexity of such systems, in this work we focus
on linear models with known configurations and perform parametric synthesis
of stabilizing digital controllers.

>>>>

\title{
Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous
Plants%
\thanks{Supported by EPSRC grant EP/J012564/1,
ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}}

@@

\begin{abstract}
%
Modern control is implemented with digital microcontrollers, embedded within
a dynamical plant that represents physical components.
%
We present a new algorithm based on counter\-example guided inductive
synthesis that automates the design of digital controllers that are
correct by construction.  The synthesis result is sound with respect to the
complete range of approximations, including time discretization,
quantization effects, and finite-precision arithmetic and its
rounding errors.
%
We have implemented our new algorithm in a tool called \tool, and are able
to automatically generate stable controllers for a set of intricate plant
models taken from the literature within minutes.
%
\end{abstract}

@@

\keywords{Control synthesis, CEGIS, finite word length, time sampling, quantization}

@@

Modern implementations of embedded control systems have proliferated with the
availability of low-cost devices that can perform highly non-trivial control
tasks, with significant impact in numerous application areas such as
environmental control and robotics~\cite{astrom1997computer, Franklin15}.
Correct control is non-trivial, however. The problem is exacerbated by
artefacts specific to digital control, such as the effects of
finite-precision arithmetic, time discretization, and quantization noise
introduced by A/D and D/A conversion.  Thus, the programming is a key
barrier to broad adoption of digital control, and requires considerable
expertise.

@@

By contrast, we leverage a very recent step-change in the scalability of
\emph{program synthesis}.  Program synthesis engines use a program
specification as the starting point, and subsequently generate a sequence of
candidate programs.  The candidate programs are iteratively refined to match
the specification more closely.  Program synthesizers that implement
Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} are now
able to generate programs for highly non-trivial specifications with a very
high degree of automation.  Modern synthesis engines combine automated
testing, genetic algorithms and SMT-based automated
reasoning~\cite{DBLP:conf/lpar/DavidKL15, DBLP:journals/corr/AlurFSS16a}.

By applying a state-of-the-art synthesis engine we are now able to present a
tool that automatically \emph{generates} digital controllers for a given
continuous plant model that are correct by construction.  This approach
promises to reduce the cost and time of development of digital control
dramatically, and requires considerably less expertise than methodologies
driven by verification.  Specifically, we synthesize controllers for hybrid
closed-loop systems, i.e., software-implemented embedded controllers along
with a model of their physical environment (the plant), that are
\emph{stable}.  Due to the complexity of such systems, in this work we focus
on linear models with known configurations and perform parametric synthesis
of stabilizing digital controllers.
